Waveform and Passive Beamforming Design for Intelligent Reflecting Surface-Aided Wireless Information and Power Transfer

### 2020-07-15 main.tex
:dizzy: R-E plot
:construction: WIT

	\begin{subsection}{Composite Channel}
		At subband $n$, denote the AP-user $k$ direct channel as $\boldsymbol{h}_{D,k,n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$, and IRS-user $k$ reflective channel as $\boldsymbol{h}_{R,k,n}^H \in \mathbb{C}^{1 \times L}$. At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection amplitude $\gamma_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$ \footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\gamma_l=1 \ \forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}. On top of this, the IRS matrix collects the reflection coefficients onto the main diagonal entries as $\boldsymbol{\Theta} = \mathrm{diag}(\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$. The IRS-aided extra link can be modeled as a concatenation of the AP-IRS channel, IRS reflection, and IRS-user channel. Hence, the composite channel for user $k$ over subband $n$ is
		\begin{equation}\label{eq:h_{k,n}}
			\boldsymbol{h}_{k,n}^H = \boldsymbol{h}_{D,k,n}^H + \boldsymbol{h}_{R,k,n}^H \boldsymbol{\Theta} \boldsymbol{H}_{I,n} = \boldsymbol{h}_{D,k,n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{k,n}
		\end{equation}
		where $\boldsymbol{\phi}=[\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{k,n}=\mathrm{diag}(\boldsymbol{h}_{R,k,n}^H)\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$. Similarly, we define $\boldsymbol{h}_k=[\boldsymbol{h}_{k,1}^T,\dots,\boldsymbol{h}_{k,N}^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{V}_k=[\boldsymbol{V}_{k,1}^T,\dots,\boldsymbol{V}_{k,N}^T]^T \in \mathbb{C}^{L \times MN}$ and let $\boldsymbol{a}_{k}=\lvert \boldsymbol{h}_{k} \rvert$, $\boldsymbol{\varsigma}_{k}=\angle{\boldsymbol{h}_{k}}$ be the magnitude and phase of the composite channel for user $k$.
	\end{subsection}

@@

						& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \sum_{m_1,m_2,m_3,m_4} \prod_{j=1,3} a_{n,m_j}s_{I,n,m_j} \prod_{j=2,4} a_{n,m_j}s_{P,n,m_j} \right)

>>>>

	\begin{subsection}{Composite Channel}
		At subband $n$, denote the AP-user $k$ direct channel as $\boldsymbol{h}_{D,k,n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$, and IRS-user $k$ reflective channel as $\boldsymbol{h}_{R,k,n}^H \in \mathbb{C}^{1 \times L}$. At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection amplitude $\gamma_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$ \footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\gamma_l=1 \ \forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}. On top of this, the IRS matrix collects the reflection coefficients onto the main diagonal entries as $\boldsymbol{\Theta} = \mathrm{diag}(\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$. The IRS-aided extra link can be modeled as a concatenation of the AP-IRS channel, IRS reflection, and IRS-user channel. Hence, the composite channel for user $k$ over subband $n$ is
		\begin{equation}\label{eq:h_{k,n}}
			\boldsymbol{h}_{k,n}^H = \boldsymbol{h}_{D,k,n}^H + \boldsymbol{h}_{R,k,n}^H \boldsymbol{\Theta} \boldsymbol{H}_{I,n} = \boldsymbol{h}_{D,k,n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{k,n}
		\end{equation}
		where $\boldsymbol{\phi}=[\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{k,n}=\mathrm{diag}(\boldsymbol{h}_{R,k,n}^H)\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$. Similarly, we define $\boldsymbol{h}_k=[\boldsymbol{h}_{k,1}^T,\dots,\boldsymbol{h}_{k,N}^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{V}_k=[\boldsymbol{V}_{k,1},\dots,\boldsymbol{V}_{k,N}] \in \mathbb{C}^{L \times MN}$ and let $\boldsymbol{a}_{k}=\lvert \boldsymbol{h}_{k} \rvert$, $\boldsymbol{\varsigma}_{k}=\angle{\boldsymbol{h}_{k}}$ be the magnitude and phase of the composite channel for user $k$.
	\end{subsection}

@@

						& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \sum_{m_1,m_2,m_3,m_4} \prod_{j=1,3} a_{n_1,m_j}s_{I,n_1,m_j} \prod_{j=2,4} a_{n_2,m_j}s_{P,n_2,m_j} \right)
